---
title: "Replication of Amit et al. (2013, Experiment 2) -- Main Analysis"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: darkly
    toc: true
    toc_float: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)

source("main_analysis_code.R")
```


# Hypothesis 1 - Social Distance and Instruction Wording (Mixed ANOVA)

## Descriptive Statistics

```{r}
replication %>% 
  summarise(
    mean_close     = mean(close),
    sd_close       = sd(close),
    median_close   = median(close),
    mean_distant   = mean(distant),
    sd_distant     = sd(distant),
    median_distant = median(distant),
    n              = n()
  )
```

```{r}
replication %>% 
  group_by(amit_wording) %>% 
  summarise(
    mean_close     = mean(close),
    sd_close       = sd(close),
    median_close   = median(close),
    mean_distant   = mean(distant),
    sd_distant     = sd(distant),
    median_distant = median(distant),
    n              = n()
  )
```

```{r}
replication %>% 
  pivot_longer(
    cols = c("close", "distant"),
    names_to = "distance",
    values_to = "picture_cards"
  ) %>% 
  ggplot(.,
         aes(
           x = picture_cards
         )) +
  facet_grid(amit_wording ~ distance) +
  geom_histogram(
    binwidth = 1
  ) +
  theme_classic()
```

## ANOVA Table and Follow-Up Analyses

```{r}
summary(h1_mixed_anova)$univariate.tests
```

### Partial Omega-Squared

```{r}
partial_omega_h1
```

### Simple Effects

```{r}
t_original
```

```{r}
t_new
```

# Sample-Specific Targets

## Manipulation Check Table

```{r}
mc_table
```

## Descriptive Statistics

```{r}
sample_specific %>% 
  summarise(
    mean_close     = mean(close),
    sd_close       = sd(close),
    median_close   = median(close),
    mean_distant   = mean(distant),
    sd_distant     = sd(distant),
    median_distant = median(distant),
    n              = n()
  )
```

```{r}
sample_specific %>% 
  group_by(amit_wording) %>% 
  summarise(
    mean_close     = mean(close),
    sd_close       = sd(close),
    median_close   = median(close),
    mean_distant   = mean(distant),
    sd_distant     = sd(distant),
    median_distant = median(distant),
    n              = n()
  )
```

```{r}
sample_specific %>% 
  pivot_longer(
    cols = c("close", "distant"),
    names_to = "distance",
    values_to = "picture_cards"
  ) %>% 
  ggplot(.,
         aes(
           x = picture_cards
         )) +
  facet_grid(amit_wording ~ distance) +
  geom_histogram(
    binwidth = 1
  ) +
  theme_classic()
```

## ANOVA Table and Follow-Ups

```{r}
summary(h1_mixed_anova_samspc)$univariate.tests
```

### Partial Omega Squared

```{r}
partial_omega_samspc
```

### Simple Effects

```{r}
t_original_samspc
```

```{r}
t_new_samspc
```

# Analysis of All Targets, with Comfort Sending Pictures as a Moderator

```{r}
all_target_model_comparison
```

```{r}
summary(log_reg_measured_inter_three)
```

## Simple Slopes

```{r}
simple_slopes_acq
```

```{r}
simple_slopes_close
```

```{r}
simple_slopes_acq %>% 
    mutate(
        org_lower = org_coef - org_se * qnorm(.975),
        org_upper = org_coef + org_se * qnorm(.975),
        new_lower = new_coef - new_se * qnorm(.975),
        new_upper = new_coef + new_se * qnorm(.975),
        org_ci    = paste(format(round(org_coef, 3), nsmall = 3), " [", format(round(org_lower, 3), nsmall = 3), ", ", format(round(org_upper, 3), nsmall = 3), "]"),
        new_ci    = paste(format(round(new_coef, 3), nsmall = 3), " [", format(round(new_lower, 3), nsmall = 3), ", ", format(round(new_upper, 3), nsmall = 3), "]")
    ) %>% 
  select(target_acq, org_ci, new_ci)
```

```{r}
simple_slopes_close %>% 
    mutate(
        org_lower = org_coef - org_se * qnorm(.975),
        org_upper = org_coef + org_se * qnorm(.975),
        new_lower = new_coef - new_se * qnorm(.975),
        new_upper = new_coef + new_se * qnorm(.975),
        org_ci    = paste(format(round(org_coef, 3), nsmall = 3), " [", format(round(org_lower, 3), nsmall = 3), ", ", format(round(org_upper, 3), nsmall = 3), "]"),
        new_ci    = paste(format(round(new_coef, 3), nsmall = 3), " [", format(round(new_lower, 3), nsmall = 3), ", ", format(round(new_upper, 3), nsmall = 3), "]")
    ) %>% 
  select(target_close, org_ci, new_ci)
```

## Main Figure

```{r, fig.height = 16, fig.width = 10}
full_plots
```

# Robustness checks

## Logistic mixed effects model with critical targets

```{r}
h1_model_comparison
```

```{r}
summary(h1_melogreg_inter)
```

## Perceived appropriateness (instead of self-reported comfort)

```{r}
approp_lrt
```

```{r}
summary(log_reg_measured_inter_three_app)
```

